Clone and graft:\\ Testing scientific applications as they are built

### 2015-01-22 turcksin-spring-mechanics/paper.tex
Fix a bug in the code and a typo in the paper.

\author{Bruno Turcksin\footnote{Department of Mathematics, Texas A\&M
    University, College Station, TX 77843-3368, USA, \url{???}}
\and
   Timo Heister\footnote{Mathematical Sciences, O-110 Martin Hall, Clemson University,
     Clemson, SC 29634-0975, USA, \url{heister@clemson.edu}}
\and
   Wolfgang Bangerth\footnote{Corresponding author. Department of Mathematics, Texas A\&M
     University, College Station, TX 77843-3368, USA, \url{bangerth@math.tamu.edu}}}

@@

\marginpar{Bruno - please update email address}
\section{Introduction}

@@

When we talk to students who just starting writing their own codes, then
they typically understand the importance of testing in some abstract
sense. But almost all of them have two fundamental misconceptions: First, that
their codes are either written well enough or will not be changed in ways
fundamental enough to suggest that these changes might break existing
functionality. And second, that doing adequate testing is just too hard and
cumbersome to be a justifiable expense of time.

>>>>

\author{Bruno Turcksin\footnote{Department of Mathematics, Texas A\&M
    University, College Station, TX 77843-3368, USA, \url{turcksin@math.tamu.edu}}
\and
   Timo Heister\footnote{Mathematical Sciences, O-110 Martin Hall, Clemson University,
     Clemson, SC 29634-0975, USA, \url{heister@clemson.edu}}
\and
   Wolfgang Bangerth\footnote{Corresponding author. Department of Mathematics, Texas A\&M
     University, College Station, TX 77843-3368, USA, \url{bangerth@math.tamu.edu}}}

@@

\section{Introduction}

@@

When we talk to students who just start writing their own codes, then
they typically understand the importance of testing in some abstract
sense. But almost all of them have two fundamental misconceptions: First, that
their codes are either written well enough or will not be changed in ways
fundamental enough to suggest that these changes might break existing
functionality. And second, that doing adequate testing is just too hard and
cumbersome to be a justifiable expense of time.
